---
title: "Cache Matrix Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

To test the functions in this assignment, we first need to source the code file:

```{r}
source('cachematrix.R')
```

## Function `makeCacheMatrix`

To create a special matrix object with `makeCacheMatrix`, we need to pass an R
matrix value to it. E.g., suppose we want to create a 2x2 matrix with the
following values:

$$x = \begin{bmatrix}
-1 & \frac{3}{2}\\
1 & -1
\end{bmatrix}$$

We can create this matrix using, for example, `rbind` and `makeCacheMatrix`:

```{r}
x <- makeCacheMatrix(rbind(c(-1, 3/2), c(1, -1)))
```

To confirm the matrix object was successfully create, we can retrieve its value
by calling the object `get` function:

```{r}
x$get()
```

The matrix object can cache the inverse of the matrix. Initially, its value is
set to `NULL`, as calling the function doesn't compute it:

```{r}
x$getInverse()
```

## Function `cacheSolve`

To compute the inverse of a matrix with `cacheSolve`, we need to pass a matrix
object created with the function `makeCacheMatrix`, as the former relies on the
attributes of the latter.

Continuing with the example matrix `x` created in the previous session, we can
simply call the function as below:

```{r}
cacheSolve(x)
```

After calling the function, we can observe that, now, the matrix object `x` has
contains the cached value of the inverse of the matrix:

```{r}
x$getInverse()
```

The secondary purpose of the function is to use cached values for the inverse of
a matrix if it's available. If we call it again, passing the same matrix `x`,
the function will echo a message saying it's using the cache value:

```{r message = TRUE}
cacheSolve(x)
```